### 2022-01-12 src-latex/parts/10-introduction.tex
Updates from Overleaf

Being active research topics, OCR and named entity recognition (NER) are still difficult tasks when applied to historical text documents.
OCR approaches used for modern documents are likely to struggle even on printed historical documents due the multiple factors related to text readability (low resolution scans, inconsistent printing rules, artifacts, show-through), document complexity (intricate and inconsistent page layout, use of ancient fonts \& special glyphs) and the variability inherent to the huge diversity of historical sources.
\bertrand{J'ai tenté un premier refactoring, pas plus techniquement précis ceci dit.}
\textcolor{green}{Phrases précedentes à reprendre avec les termes adéquats + ajouter une ref.}
On the other hand, NER approaches developed for modern texts suffer from the time gap between the contemporary entities and the entities mentioned in older texts and from the errors introduced into the text by the OCR step.\textcolor{green}{ajouter une ref}

>>>>

Being active research topics, OCR and named entity recognition (NER) are still difficult tasks when applied to historical text documents.
OCR approaches used for modern documents are likely to struggle even on printed historical documents due the multiple factors related to text readability (low resolution scans, inconsistent printing rules, artifacts, show-through), document complexity (intricate and versatile page layout, use of ancient fonts \& special glyphs) and the variability inherent to the huge diversity of historical sources.
\bertrand{J'ai tenté un premier refactoring, pas plus techniquement précis ceci dit.}
\nathalie{Phrases précedentes à reprendre avec les termes adéquats + ajouter une ref.}
On the other hand, NER approaches developed for modern texts suffer from the time gap between the contemporary entities and the entities mentioned in older texts and from the errors introduced into the text by the OCR step.\nathalie{ajouter une ref}

### 2022-01-12 src-latex/parts/20-related-work.tex
Updates from Overleaf

% !TeX root = ../main-paper.tex
\section{OCR and NER on Historical Texts}

@@

\subsection{Optical Character Recognition on Historical Texts}

@@

\textcolor{green}{à compléter/retoucher}

@@

Many approaches have been designed to recognize named entities, ranging from handcrafted rules to supervised approaches \cite{nadeau2007}. Rule based approaches look for portions of text that match patterns based on word characteristics such as their case, whether they are digits or not, their part-of-speech tags, etc. These patterns can be fully handcrafted like in \cite{bell2020automated} or generated by data mining approaches like in \cite{nouvel2011}. Rule based approaches can also combine a set of patterns with a set of dictionaries (gazetteers, author lists, etc.) that help recognizing named entities when an exhaustive lexicon of searched entities is available \cite{mansouri2008,maurel2011}. For example, the CasEN\footnote{\url{https://tln.lifat.univ-tours.fr/version-francaise/ressources/casen}} transducer cascade leverages syntatic lexical patterns and dictionnaries to recognize Named Entities in French texts. Such kind of approaches achieve very good results when applied to specialized domain corpus - like directories - and when an exhaustive lexicon are available, but at high system engineering cost \cite{nadeau2007}.

@@

\subsection{Named Entity Recognition in Historical Texts}

\cite{Labusch2020NamedED} applied a BERT-based NER model to historical texts in German, French, and English, produced by OCR. It is off-the-shelf multilingual BERT-based NER model, pretrained on more than 2 000 000 pages of OCRed historical texts in three languages and fine-tuned on historical texts NER ground truth, also in three languages. Eventually, a clear decrease in NER performance on OCRised texts is noted. Moreover, the article reports that this decrease is more important for English texts for which the OCR is of poorer quality than for texts in the other two languages.

Several recent studies have focused on the extent to which the quality of the OCR affects the results produced by a NER model.\cite{van2020assessing} assess the impact of OCR on several NLP downstream tasks, including NER. They worked on a corpus published by a post-OCR correction software company, made of many journal articles with different levels of OCR errors and their respective groundtruths. For each OCRed article, the Word Error Rate (WER) is computed and the English model \textit{en-core-web-lg} provided by Spacy\footnote{\url{https://spacy.io/}} library is used to perform NER on \textit{Person}, \textit{GPE} and \textit{Date}. The performance of the NER model with respect to OCR quality is eventually assessed by calculating the F-measure for each NER class, and each article i.e., each WER value. \cite{hamdi2020assessing} performed a similar but more extensive evaluation on four different NER models: CoreNLP using Conditional Random Fields and three deep neural models, BLSTM-CNN, BLSTM-CRF, and BLSTM-CNN-CRF. They tested them on two well-known NER benchmark corpora: CoNLL-02 and CoNLL-03. They applied four different types of OCR noise to each corpus, with two levels of degradation and computed the WER and Character Error Rate (CER) for each degraded version. Finally, they applied each NER model to the progressively degraded versions of the corpus and computed the resulting F-measure. Overall, NER F-mesure drops from 90\% to 50\% when the WER increase from 8\% to 50\%. Besides, all NER models are sensitive to OCR errors, but models based on deep neural networks seem less prone to errors.

Based on the observation that OCR errors necessarily affect the performance of NER models applied to historical texts, \cite{huynh2020use} and \cite{marz2021data} have proposed different approaches to reduce their negative impact. The former uses a spelling correction tool on several corpora with variable OCR error rates, to assess whether spelling correction has a beneficial impact on NER performance or not. The results showed that as long as OCR errors remain low (CER<2\% and WER<10\%), the F-measure of NER results remains stable. It starts to decrease significantly when OCR errors exceed these thresholds. The latter work focuses on adapting the training data to facilitate the generalisation of an off-the-shelf NER model from modern texts to historical texts. Three different NER models are tested on three historical corpora, in French, English, and Dutch. The best results are produced by a model trained on clean modern data, including many  embeddings as input (FastText, character and multilingual Flair embeddings, BERT and historical embeddings computed with Flair on a historical corpus), and fine-tuned on a noisy historical groundtruth.

>>>>

% !TeX root = ../main-paper.tex
\section{OCR and NER on historical texts}

@@

\subsection{Optical Character Recognition on historical texts}

@@

\nathalie{à compléter/retoucher}

@@

Many approaches have been designed to recognize named entities, ranging from handcrafted rules to supervised approaches \cite{nadeau2007}. Rule based approaches look for portions of text that match patterns based on word characteristics such as their case, whether they are digits or not, their part-of-speech tags, etc. These patterns can be fully handcrafted like in \cite{bell2020automated} or generated by data mining approaches like in \cite{nouvel2011}. Rule based approaches can also combine a set of patterns with a set of dictionaries (gazetteers, author lists, etc.) that help recognizing named entities when an exhaustive lexicon of searched entities is available \cite{mansouri2008,maurel2011}. For example, the CasEN\footnote{\url{https://tln.lifat.univ-tours.fr/version-francaise/ressources/casen}} transducer cascade leverages syntactic lexical patterns and dictionaries to recognize Named Entities in French texts. Such kind of approaches achieve very good results when applied to specialized domain corpus - like directories - and when an exhaustive lexicon are available, but at high system engineering cost \cite{nadeau2007}.

@@

\subsection{Named Entity Recognition on historical texts}

\cite{Labusch2020NamedED} applied a BERT-based NER model to historical texts in German, French, and English, produced by OCR. It is off-the-shelf multilingual BERT-based NER model, pretrained on more than 2 000 000 pages of OCRed historical texts in three languages and fine-tuned on historical texts NER ground truth, also in three languages. Eventually, a clear decrease in NER performance on OCRed texts is noted. Moreover, the article reports that this decrease is more important for English texts for which the OCR is of poorer quality than for texts in the other two languages.

Several recent studies have focused on the extent to which the quality of the OCR affects the results produced by a NER model.\cite{van2020assessing} assess the impact of OCR on several NLP downstream tasks, including NER. They worked on a corpus published by a post-OCR correction software company, made of many journal articles with different levels of OCR errors and their respective ground truths. For each OCRed article, the Word Error Rate (WER) is computed and the English model \textit{en-core-web-lg} provided by Spacy\footnote{\url{https://spacy.io/}} library is used to perform NER on \textit{Person}, \textit{GPE} and \textit{Date}. The performance of the NER model with respect to OCR quality is eventually assessed by calculating the F-measure for each NER class, and each article i.e., each WER value. \cite{hamdi2020assessing} performed a similar but more extensive evaluation on four different NER models: CoreNLP using Conditional Random Fields and three deep neural models, BLSTM-CNN, BLSTM-CRF, and BLSTM-CNN-CRF. They tested them on two well-known NER benchmark corpora: CoNLL-02 and CoNLL-03. They applied four different types of OCR noise to each corpus, with two levels of degradation and computed the WER and Character Error Rate (CER) for each degraded version. Finally, they applied each NER model to the progressively degraded versions of the corpus and computed the resulting F-measure. Overall, NER F-score drops from 90\% to 50\% when the WER increase from 8\% to 50\%. Besides, all NER models are sensitive to OCR errors, but models based on deep neural networks seem less prone to errors.

Based on the observation that OCR errors necessarily affect the performance of NER models applied to historical texts, \cite{huynh2020use} and \cite{marz2021data} have proposed different approaches to reduce their negative impact. The former uses a spelling correction tool on several corpora with variable OCR error rates, to assess whether spelling correction has a beneficial impact on NER performance or not. The results showed that as long as OCR errors remain low (CER<2\% and WER<10\%), the F-measure of NER results remains stable. It starts to decrease significantly when OCR errors exceed these thresholds. The latter work focuses on adapting the training data to facilitate the generalization of an off-the-shelf NER model from modern texts to historical texts. Three different NER models are tested on three historical corpora, in French, English, and Dutch. The best results are produced by a model trained on clean modern data, including many  embeddings as input (FastText, character and multilingual Flair embeddings, BERT and historical embeddings computed with Flair on a historical corpus), and fine-tuned on a noisy historical ground truth.

### 2022-01-12 src-latex/parts/40-ner-approaches.tex
Updates from Overleaf

\paragraph{Regexp}
::TODO::

\paragraph{Spacy 3 transition-based NER.}
The \textit{of the shelf} NLP library SpaCY offers a named entity recognition tool based on an ad hoc architecture which has not been yet published but is explained by the developers on their website. Although the latest version of SpaCy (v3) leverages BERT models, we could not use them as no NER pipeline is available for the French language at the time of our experiments\footnote{https://spacy.io/models/fr}. The vanilla NER pipeline is two-fold. Words are first encoded into local context-aware embeddings using a window-based CNN similar to~\cite{collobert2011}. The decision layer is an adaptation of the transition-based model presented in~\cite{lample2016}. As words are processed sequentially, their vectors are concatenated with those in the last known entities to encode the nearby predicted semantics as a dynamic attention mechanism. The classification layer relies on a finite-state machine whose transition probabilities are learned using a multi-layer perceptron.
In 2018~\cite{won2018} compared SpaCy's vanilla NER performances on historical texts about places with several other software packages (Stanford-NER, Ner-Tagger, Edinburgh Geopoarser and Polyglot). Results showed SpaCy to be average with a F1-score of 0.57. The SpaCy developers claims an accuracy of 0.85 for the English NER pipeline \textit{en\_core\_web\_lg} on the OntoNotes 5.0 corpus\footnote{https://spacy.io/usage/facts-figures}.

\paragraph{CamemBERT \& CamemBERT+pretraining on historical directories}
::TODO::

>>>>

\subsubsection{Regexp}
::TODO::
Needed for experiment 2 ?

\subsubsection{Spacy 3 NER pipeline}
The \textit{of the shelf} NLP library SpaCY offers a named entity recognition tool based on an ad hoc architecture which has not been yet published but is explained by the developers on their website. Although the latest version of SpaCy (v3) leverages BERT models, we could not use them as no NER pipeline is available for the French language at the time of our experiments\footnote{https://spacy.io/models/fr}. The vanilla NER pipeline is two-fold. Words are first encoded into local context-aware embeddings using a window-based CNN similar to~\cite{collobert2011}. The decision layer is an adaptation of the transition-based model presented in~\cite{lample2016}. As words are processed sequentially, their vectors are concatenated with those in the last known entities to encode the nearby predicted semantics as a dynamic attention mechanism. The classification layer relies on a finite-state machine whose transition probabilities are learned using a multi-layer perceptron.
In 2018~\cite{won2018} compared SpaCy's vanilla NER performances on historical texts about places with several other software packages (Stanford-NER, Ner-Tagger, Edinburgh Geopoarser and Polyglot). Results showed SpaCy to be average with a F1-score of 0.57. The SpaCy developers claims an accuracy of 0.85 for the English NER pipeline \textit{en\_core\_web\_lg} on the OntoNotes 5.0 corpus\footnote{https://spacy.io/usage/facts-figures}.

\subsubsection{CamemBERT \& CamemBERT+pretrained on raw entries}
::TODO::

### 2022-01-12 src-latex/parts/80-conclusion.tex
Setup paper structure
Updates from Overleaf

% !TeX root = ../main-paper.tex
\section{Results}

>>>>

% !TeX root = ../main-paper.tex
\section{Conclusion}

Ideas for future work:
\begin{itemize}
    \item Evaluate this: fine-tune Spacy NER on a few samples to generated a bootstrap dataset, feed it to BERT (cleaned or raw) to create an good model with minimal efforts ?
    \item Use ML to infer regexes ?
    \item As directories entries are always structured the same way (in a given list at least): use NER to identify entries within pages to save the burden of having to rely on the page layout ?
\end{itemize}
